Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-26 paper.qmd
Edit csv and table code, fix #41

```{r}
#| label: tbl-trip-purposes
# For PDF:
knitr::kable(trip_purposes, caption = "Trip purposes used in the CRUSE Tool.", booktabs = TRUE) |>
  kableExtra::kable_styling(latex_options = "striped", full_width = FALSE) |>
  kableExtra::column_spec(1, width = "13em") |>
  kableExtra::column_spec(2, width = "15em") |>
  kableExtra::column_spec(3, width = "12em") |>
  kableExtra::column_spec(4, width = "5em")
# For HTML:
# knitr::kable(trip_purposes, caption = "Trip purposes used in the CRUSE Tool.")
```

>>>>

```{r}
#| label: tbl-trip-purposes
# For PDF:
knitr::kable(trip_purposes, caption = "Trip purposes used in the CRUSE Tool.", booktabs = TRUE) |>
  kableExtra::kable_styling(latex_options = "striped", full_width = FALSE, font_size = 8) |>
  kableExtra::column_spec(1, width = "5em") |>
  kableExtra::column_spec(2, width = "12em") |>
  kableExtra::column_spec(3, width = "15em") |>
  kableExtra::column_spec(4, width = "15em")
# For HTML:
# knitr::kable(trip_purposes, caption = "Trip purposes used in the CRUSE Tool.")
```

### 2024-03-26 paper.tex
Edit csv and table code, fix #41

@@

\\
\toprule
Trip purpose & Description & Primary source(s) & Confidence\\
\midrule
\cellcolor{gray!10}{Work (commute)} & \cellcolor{gray!10}{Commuting to/from workplaces} & \cellcolor{gray!10}{Census 2016 POWSCAR Data} & \cellcolor{gray!10}{High confidence - data both origins and destinations for trip purposes}\\
Primary Education & Primary school trips & Census 2016 POWSCAR Data & Dept. of Education Schools database,High confidence - data both origins and destinations for trip purposes\\
\cellcolor{gray!10}{Secondary Education} & \cellcolor{gray!10}{Secondary school trips} & \cellcolor{gray!10}{Census 2016 POWSCAR Data} & \cellcolor{gray!10}{Dept. of Education Schools database,High confidence - data both origins and destinations for trip purposes}\\
Tertiary Education & Tertiary education trips & Census 2016 POWSCAR Data - Geodirectory categories for 'Tertiary Education' and 'Other Education' & High confidence - data both origins and destinations for trip purposes\\
\cellcolor{gray!10}{Social} & \cellcolor{gray!10}{NHTS classification, including trips to/from sports facilities, leisure, and cultural destinations (e.g. restaurants, cinemas, gyms etc.)} & \cellcolor{gray!10}{Trip rates from NHTS} & \cellcolor{gray!10}{Geodirectory businesses classified according to relevant NACE codes,"Medium Confidence - Method should identify clusters of activity for this trip purpose, although individual trips or destinations come with significant uncertainty"}\\
\addlinespace
Shopping & NHTS classification, including trips to/from supermarkets and shops & Trip rates from NHTS & Geodirectory businesses classified according to relevant NACE codes,"Medium Confidence - Method should identify clusters of activity for this trip purpose, although individual trips or destinations come with significant uncertainty"\\
\cellcolor{gray!10}{Personal/other} & \cellcolor{gray!10}{Combination of two NHTS classifications, and includes trips to medical, personal services and others} & \cellcolor{gray!10}{Trip rates from NHTS} & \cellcolor{gray!10}{Geodirectory businesses classified according to relevant NACE codes,"Medium Confidence - Method should identify clusters of activity for this trip purpose, although individual trips or destinations come with significant uncertainty"}\\
Tourism/recreational & Trips by non-resident visitors to/from visitor attractions & Geodirectory listings for accommodation (origins) and destinations (destinations) & Failte Ireland accommodation database, Failte Ireland attraction database,Low confidence - lack of data regarding tourist trip rates\\
\cellcolor{gray!10}{Public Transport} & \cellcolor{gray!10}{Trips to/from public transport} & \cellcolor{gray!10}{NTA Heavy Rail Census} & \cellcolor{gray!10}{NA}\\
\bottomrule

@@

>>>>

\begingroup\fontsize{8}{10}\selectfont

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{15em}>{\raggedright\arraybackslash}p{15em}}

@@

\\
\toprule
Trip purpose & Description & Primary source(s) & Confidence\\
\midrule
\cellcolor{gray!10}{Work (commute)} & \cellcolor{gray!10}{Commuting to / from workplaces} & \cellcolor{gray!10}{Census 2016 POWSCAR Data} & \cellcolor{gray!10}{High confidence - data both origins and destinations for trip purposes}\\
Primary Education & Primary school trips & Census 2016 POWSCAR Data, Schools database & High confidence - data both origins and destinations for trip purposes\\
\cellcolor{gray!10}{Secondary Education} & \cellcolor{gray!10}{Secondary school trips} & \cellcolor{gray!10}{Census 2016 POWSCAR Data, Schools database} & \cellcolor{gray!10}{High confidence - data both origins and destinations for trip purposes}\\
Tertiary Education & Tertiary education trips & Census 2016 POWSCAR Data - Geodirectory categories & High confidence - data both origins and destinations for trip purposes\\
\cellcolor{gray!10}{Social} & \cellcolor{gray!10}{NHTS classification (e.g. restaurants, cinemas, gyms etc.)} & \cellcolor{gray!10}{Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes} & \cellcolor{gray!10}{Medium Confidence}\\
\addlinespace
Shopping & NHTS classificationfrom supermarkets and shops & Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes & Medium Confidence\\
\cellcolor{gray!10}{Personal / other} & \cellcolor{gray!10}{Combination of two NHTS classifications, and includes trips to medical, personal services and others} & \cellcolor{gray!10}{Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes} & \cellcolor{gray!10}{Medium Confidence}\\
Tourism / recreational & Trips by non-resident visitors to / from visitor attractions & Geodirectory listings for accommodation (origins) and destinations (destinations) & Failte Ireland accommodation database, Failte Ireland attraction database\\
\bottomrule

@@

\endgroup{}
